Joint analysis of read count data

### 2020-09-11 combined_analysis/combine_all_DLPFC.Rmd
Inital commit

@@

>>>>

### Create residuals
```{r Create residuals}

form = ~ Dx*Reported_Gender + RIN + ageOfDeath + scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate)

residuals.lst = lapply( vobj.lst, function(vobj){

  # Compute residuals which adding back Diagnosis and Sex effects
  resid.lst = fitVarPartModel(vobj, form, info, fxn = function(fit){
    residuals(fit) + get_prediction( fit, ~ Dx*Reported_Gender)
    }, BPPARAM = SnowParam(18))  
  do.call(rbind, resid.lst)
  })
names(residuals.lst) = names(vobj.lst)
```

@@

# Create residuals using fitVarPart and get_prediction()
